Comparison of Catalogs

### 2024-07-28 compare/compare.qmd
percent_desc_histogram

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')

@@

```{python}
def relative_diff(hec, lcv):
    diff = (hec - lcv) *100/ hec
    diff[np.isinf(diff)] = np.nan
    return diff
```

@@

```{python}
#| echo: false

@@

```{python}
dt["diff_T"] = relative_diff(dt["T"], dt["TType"])
dt["diff_T"].info("stats")
```

```{python}
sigma_T = sigma_clip(dt["diff_T"])
sigma_T.info("stats"), dt["diff_T"].info("stats")
```

```{python}
sns.histplot(dt["diff_T"], kde = True, label="Unclipped data")
sns.histplot(sigma_T, kde = True, label = "Sigma=3")
plt.title("Percentage change Distribution [%]")
plt.xlim([-200, 200])
plt.xlabel("Types of Galaxies")
plt.legend()
plt.show()
```

As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

@@

```{python}
dt["diff_inc"] = relative_diff(dt["INCL"], dt["inc"])
dt["diff_inc"].info("stats") 
```

```{python}
sns.histplot(dt["diff_inc"], kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"Inclination of the galaxies [{dt['inc'].unit}]")
plt.show()
```

>>>>

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')
pd.set_option('display.float_format', lambda x: '%.f' % x)

@@

```{python}
def relative_diff(hec, lcv):
    """
    Calculate the relative difference between two sets of values.

    Parameters:
    hec (numpy.ndarray): An array of values representing the HEC dataset.
    lcv (numpy.ndarray): An array of values representing the LCV dataset.

    Returns:
    numpy.ndarray: An array of relative differences between the HEC and LCV datasets.
    The relative difference is calculated as ((HEC - LCV) * 100) / |HEC|.
    Any infinite values in the result are replaced with NaN.
    """
    diff = (hec - lcv) * 100 / np.abs(hec)
    diff[np.isinf(diff)] = np.nan
    return diff

def percent_desc_histogram(x, sigmaclip = True, zoom = None):
    """
    This function creates a histogram of the given data and optionally applies a 3-sigma clip.

    Parameters:
    - x (array-like): The input data to create the histogram.
    - sigmaclip (bool, optional): Whether to apply a 3-sigma clip to the data. Default is True.
    - zoom (tuple, optional): The range of values to display on the x-axis of the histogram. Default is None.

    Returns:
    - t_pd (DataFrame): A pandas DataFrame containing statistical information about the input data.

    The function uses the seaborn library to create the histogram and applies a 3-sigma clip if `sigmaclip` is True.
    The histogram is displayed with appropriate labels and titles.
    The statistical information about the input data is returned as a pandas DataFrame.
    """
    plt.close()
    temp_table = QTable()
    temp_table["Percentage change"]= x.copy()

    if sigmaclip is True:
        temp_table["Percentage change, after 3 sigma clip"] = sigma_clip(temp_table["Percentage change"],3)

    t_pd = temp_table.to_pandas()

    sns.histplot(temp_table["Percentage change"], kde = True, label = "Percentage change")

    if sigmaclip is True:
        sns.histplot(temp_table["Percentage change, after 3 sigma clip"], kde = True, label = "Percentage change, after 3 sigma clip")

    plt.xlim(zoom)
    plt.xlabel("Percentage change Distribution [%]")
    plt.title("Types of Galaxies")
    plt.legend()
    plt.show()

    return t_pd.describe(percentiles=[]).map('{:,.0f}'.format).style.set_properties(**{'text-align': 'center'})
```

@@

```{python}
dt["INCL"].mask = np.isnan(dt["INCL"])
```
```{python}
#| echo: false

@@

dt["diff_T"] = relative_diff(hec = dt["T"], lcv = dt["TType"])
percent_desc_histogram(dt["diff_T"], zoom = [-200,200])
```

@@

```{python}
dt["INCL"].mask
```
```{python}
dt["diff_inc"] = relative_diff(hec = dt["INCL"],lcv = dt["inc"])
percent_desc_histogram(dt["diff_inc"])
```

```{python}
#k = sigma_clip(dt["diff_inc"])
dt["diff_T"].info
```
